### 2016-11-18 src/abstract.tex
foo

The \textsc{\CARPOOL{}} problem is a star packing problem in
directed graphs.
Formally, given a directed graph $G = (V, E)$,
a capacity function $ c: V \rightarrow \N $,
and a weight function $w : E \rightarrow \R $,
a feasible \emph{carpool matching} is a triple 
$(P, D, M)$, where $P$ and $D$ form a partition of $V$, 
and $M$ is a subset of $E \cap (P \times D)$,
under the constraints that for every vertex $d \in D$, 
$\din(d) \leq c(d)$, 
and for every vertex $p \in P$, $\dout(p) \leq 1$.
In the \textsc{\CARPOOL{}} 
problem we seek for a matching $(P, D, M)$ that maximizes the total weight of $M$.

The problem arises when designing an online carpool service, 
such as Zimride~\cite{zimride}, 
that tries to connect between passengers and drivers based on (arbitrary) similarity function.
The problem is known to be NP-hard, 
even for undirected graphs, uniform weights and without capacity constraints.

We present a $2$-approximation algorithm for the problem,
the currnet best known approximation ratio.
Also, when the maximum capacity, $C$, is constant we give a
$\frac{C + 1}{2C}$-approximation algorithms for the 
unweighted variant of the problem, 
improving over the bset known approximation ratio for the special case where $C = 2$.

>>>>

The \textsc{\CARPOOL{}} problem is a star packing problem in directed graphs.
Formally, given a directed graph $G = (V, A)$,
a capacity function $ c: V \rightarrow \N $,
and a weight function $w : A \rightarrow \R $,
a feasible \emph{carpool matching} is a triple 
$(P, D, M)$, where $P$ (passengers) and $D$ (drivers) form a partition of $V$, 
and $M$ is a subset of $A \cap (P \times D)$,
under the constraints that for every vertex $d \in D$, 
$\din(d) \leq c(d)$, 
and for every vertex $p \in P$, $\dout(p) \leq 1$.
In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
total weight of $M$.

The problem arises when designing an online carpool service, 
such as Zimride~\cite{zimride}, 
that tries to connect between passengers and drivers based on (arbitrary) similarity function.
The problem is known to be NP-hard, 
even for uniform weights and without capacity constraints.

we show that the problem can be formulated as
unconstarints submodular maximization problem, 
thus it has a 2-approximation algorithm.
For the unweighted variant of the problem when the maximum possible capacity, $C$, is
fixed, we give a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm
for the any $\varepsilon > 0$.
